Pillar 2 - Topic Modeling

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
simplify merge of catalogues and manuals

If we trained separately but with the same number of topics, and wish to merge and save them:
```{r merge if trained separately, eval = TRUE}
cata <- catalogues_topic_model$n_topic
man  <- manuals_topic_model$n_topic

tb_topic_model <- tibble()

if(all(cata == man)){
  tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
}

@@

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin, data = tb_topic_model){

@@

##Best model
We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with more burns and iterations
```{r best model, eval = T}
catalogues_tm <- tb_topic_model %>% fil
catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]

>>>>

If we trained separately and wish to merge into a single tibble: 
```{r merge if trained separately, eval = TRUE}
tb_topic_model <- tibble()

if(exists("manuals_topic_model") && exists("catalogues_topic_model")){
  tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
} else  if(exists("catalogues_topic_model")){
  tb_topic_model <- catalogues_topic_model 
  } else if (exists("manuals_topic_model")){
    tb_topic_model <- catalogues_topic_model
}

@@

##Plots - Model Evaluation CHANGE TO CONFERENCE CODE
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin, data = tb_topic_model){

@@

##Best model
We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
```{r best model, eval = T}
catalogues_tm <- tb_topic_model %>% filter()
catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]
